---
title: "narratives_code_final"
author: "sara alassaf"
date: "2026-03-31"
output: html_document
---

```{r}
# -----------------------------
# Load libraries
# -----------------------------
library(readr)
library(dplyr)
library(tidyr)
library(WDI)
library(countrycode)
library(purrr)
library(fixest)
library(zoo)
library(pracma)
library(haven)
library(lubridate)
library(stringr)
```

```{r}
# -----------------------------
# Load base
# -----------------------------
df <- read_csv("base_final.csv") %>%
  mutate(
    year = as.integer(substr(year_month, 1, 4)),
    country = toupper(country)
  )

countries_needed <- sort(unique(df$country))

# -----------------------------
# World Bank 
# -----------------------------

wb_indicators <- c(
  internet       = "IT.NET.USER.ZS")


wb_list <- purrr::imap(wb_indicators, function(code, name) {
  WDI(country = countries_needed, indicator = code) %>%
    transmute(
      country = toupper(iso2c),
      year,
      !!name := .data[[code]]
    )
})

wb <- purrr::reduce(wb_list, full_join, by = c("country", "year"))


# -----------------------------
# SWIID (names -> ISO2)
# -----------------------------
swiid <- read_csv("swiid.csv") %>%
  mutate(
    country = toupper(countrycode(country, "country.name", "iso2c"))
  ) %>%
  filter(country %in% countries_needed) %>%
  transmute(country, year, gini_disp, gini_mkt)

# -----------------------------
# Merge
# -----------------------------
df2 <- df %>%
  left_join(wb, by = c("country", "year")) %>%
  left_join(swiid, by = c("country", "year"))
```

There are two approaches, one with country-year specific effects and other with yearly control data on gdp, inequality and internet access.

```{r}
vars_annual <- c("internet", "gini_disp", "gini_mkt")

df_monthly <- df2 %>%
  mutate(
    ym = as.Date(paste0(year_month, "-01")),
    t = as.numeric(ym),
    month = as.integer(substr(year_month, 6, 7))
  ) %>%
  arrange(country, ym) %>%
  group_by(country) %>%
  mutate(
    across(all_of(vars_annual), ~{
      x_raw <- as.numeric(.x)


      x <- x_raw
      x[month != 12] <- NA_real_

 
      dec_idx <- which(month == 12)
      x_dec <- x[dec_idx]

      last_val <- NA_real_
      last_delta <- NA_real_

      for (i in seq_along(x_dec)) {
        if (!is.na(x_dec[i])) {
          if (!is.na(last_val)) {
            d <- x_dec[i] - last_val
            if (d != 0) last_delta <- d
          }
          last_val <- x_dec[i]
        } else if (!is.na(last_val)) {
          if (is.na(last_delta)) last_delta <- 0
          x_dec[i] <- last_val + last_delta
          last_val <- x_dec[i]
        }
      }

      x[dec_idx] <- x_dec

     
      keep <- !is.na(x)
      if (sum(keep) >= 2) {
        tt <- t[keep]
        yy <- x[keep]
        pchip(tt, yy, t)
      } else {
        x
      }
    })
  ) %>%
  ungroup() %>%
  select(-ym, -t, -month)
```

```{r}
narratives <- c(
  "Restrictive_equal_opportunities_rate",
  "Restrictive_fairness_rate",
  "Restrictive_meritocracy_rate",
  "Restrictive_redistribution_rate",
  "Permissive_equal_opportunities_rate",
  "Permissive_fairness_rate",
  "Permissive_meritocracy_rate",
  "Permissive_redistribution_rate"
)

vars_levels <- c(
  narratives,
  "HHI",
  "ENP",
  "Top1",
  "Top3",
  "Top5",
  "Entropy",
  "TailShare",
  "internet",
  "gini_disp",
  "gini_mkt",
  "G_Trends"
)


df_base_levels_m <- df_monthly %>%
  mutate(year = as.integer(substr(year_month, 1, 4)))
```

```{r}
run_lags_diff_m <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable = var,
      lag      = L,
      coef     = ct["p_lag", "Estimate"],
      p_value  = ct["p_lag", "Pr(>|t|)"],
      n        = nobs(m),
      spec     = "full_diff_rf"
    )
  })
}
```

```{r}
run_lags_hybrid_m <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        N_lag = lag(.data[[var]], L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(N_lag),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ N_lag + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable = var,
      lag      = L,
      coef     = ct["N_lag", "Estimate"],
      p_value  = ct["N_lag", "Pr(>|t|)"],
      n        = nobs(m),
      spec     = "hybrid_rf"
    )
  })
}
```


```{r}
all_lags_diff_m <- purrr::map_dfr(narratives, run_lags_diff_m)

all_lags_hybrid_m <- purrr::map_dfr(narratives, run_lags_hybrid_m)

all_lags_compare_m <- bind_rows(
  all_lags_diff_m,
  all_lags_hybrid_m
)

significant_compare_m <- all_lags_compare_m %>%
  filter(p_value < 0.1)
```

```{r}
iv_vars <- c("HHI", "ENP", "Top1", "Top3", "Top5", "Entropy", "TailShare")

run_iv_lag <- function(variable, lag){

  purrr::map_dfr(iv_vars, function(iv){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[variable]] - lag(.data[[variable]]),
        dIV   = .data[[iv]] - lag(.data[[iv]]),
        p_lag  = lag(dN,  lag),
        iv_lag = lag(dIV, lag)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(iv_lag)
      )

    # First stage: ΔN_{t-L} ~ ΔIV_{t-L}
    fs <- feols(
      p_lag ~ iv_lag | country^year + year_month,
      data = d,
      cluster = ~country
    )

    ct_fs <- summary(fs)$coeftable
    t_excl <- ct_fs["iv_lag", "t value"]
    f_excl <- as.numeric(t_excl)^2

    # Second stage: ΔG_t ~ ΔN̂_{t-L}
    ivm <- feols(
      dG ~ 1 | country^year + year_month | p_lag ~ iv_lag,
      data = d,
      cluster = ~country
    )

    ct <- summary(ivm)$coeftable

    tibble(
      variable      = variable,
      lag           = lag,
      instrument    = iv,
      F_first_stage = as.numeric(f_excl),
      coef_iv       = ct["fit_p_lag", "Estimate"],
      p_value       = ct["fit_p_lag", "Pr(>|t|)"],
      n             = nobs(ivm)
    )
  })
}
```

```{r}
results_iv_all <- expand.grid(
  variable = narratives,
  lag = 1:12,
  stringsAsFactors = FALSE
) %>%
  purrr::pmap_dfr(~ run_iv_lag(..1, ..2))

strong_iv_results <- results_iv_all %>%
  filter(F_first_stage > 5, p_value < 0.1) %>%
  arrange(desc(abs(coef_iv)))
```

The IV above is the original, and does not include cov_controls (internet, gini_disp). The version below does. Both are differenced.

```{r}
# ============================================================
# DIFFERENCED IV (DV, endogenous regressor, and IV all differenced)
# ============================================================
cov_controls <- c("internet", "gini_disp")
run_iv_lag_diff <- function(variable, lag){

  purrr::map_dfr(iv_vars, function(iv){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG = G_Trends - lag(G_Trends, 1),
        dN = .data[[variable]] - lag(.data[[variable]], 1),
        dZ = .data[[iv]] - lag(.data[[iv]], 1),

        dN_lag = lag(dN, lag),
        dZ_lag = lag(dZ, lag)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(dN_lag),
        !is.na(dZ_lag)
      )

    # -------------------
    # FIRST STAGE (differences)
    # -------------------

    fs_fml <- as.formula(
      paste0(
        "dN_lag ~ dZ_lag",
        if(length(cov_controls) > 0) paste0(" + ", paste(cov_controls, collapse = " + ")) else "",
        " | country^year + year_month"
      )
    )

    fs <- feols(
      fs_fml,
      data = d,
      cluster = ~country
    )

    ct_fs  <- summary(fs)$coeftable
    t_excl <- ct_fs["dZ_lag", "t value"]
    F_fs   <- as.numeric(t_excl)^2

    # -------------------
    # SECOND STAGE (differences)
    # -------------------

    rhs_controls <- if(length(cov_controls) > 0) paste(cov_controls, collapse = " + ") else "1"

    iv_fml <- as.formula(
      paste0(
        "dG ~ ", rhs_controls,
        " | country^year + year_month",
        " | dN_lag ~ dZ_lag"
      )
    )

    ivm <- feols(
      iv_fml,
      data = d,
      cluster = ~country
    )

    ct <- summary(ivm)$coeftable

    tibble(
      variable      = variable,
      lag           = lag,
      instrument    = iv,
      F_first_stage = F_fs,
      coef_iv       = ct["fit_dN_lag", "Estimate"],
      p_value       = ct["fit_dN_lag", "Pr(>|t|)"],
      n             = nobs(ivm)
    )
  })
}

# Run
iv_results_diff <- expand.grid(
  variable = narratives,
  lag      = 1:12,
  stringsAsFactors = FALSE
) %>%
  purrr::pmap_dfr(~ run_iv_lag_diff(..1, ..2))

iv_hits_diff <- iv_results_diff %>%
  filter(F_first_stage > 10, p_value < 0.1) %>%
  arrange(desc(F_first_stage), p_value)

iv_hits_diff
```

```{r}
# ============================================================
# HYBRID IV (DV differenced; endogenous regressor and IV in levels)
# ============================================================

run_iv_lag_hybrid <- function(variable, lag){

  purrr::map_dfr(iv_vars, function(iv){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends, 1),
        N_lag = lag(.data[[variable]], lag),
        Z_lag = lag(.data[[iv]], lag)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(N_lag),
        !is.na(Z_lag)
      )

    # -------------------
    # FIRST STAGE (levels)
    # -------------------

    fs_fml <- as.formula(
      paste0(
        "N_lag ~ Z_lag",
        if(length(cov_controls) > 0) paste0(" + ", paste(cov_controls, collapse = " + ")) else "",
        " | country^year + year_month"
      )
    )

    fs <- feols(
      fs_fml,
      data = d,
      cluster = ~country
    )

    ct_fs  <- summary(fs)$coeftable
    t_excl <- ct_fs["Z_lag", "t value"]
    F_fs   <- as.numeric(t_excl)^2

    # -------------------
    # SECOND STAGE (hybrid)
    # -------------------

    rhs_controls <- if(length(cov_controls) > 0) paste(cov_controls, collapse = " + ") else "1"

    iv_fml <- as.formula(
      paste0(
        "dG ~ ", rhs_controls,
        " | country^year + year_month",
        " | N_lag ~ Z_lag"
      )
    )

    ivm <- feols(
      iv_fml,
      data = d,
      cluster = ~country
    )

    ct <- summary(ivm)$coeftable

    tibble(
      variable      = variable,
      lag           = lag,
      instrument    = iv,
      F_first_stage = F_fs,
      coef_iv       = ct["fit_N_lag", "Estimate"],
      p_value       = ct["fit_N_lag", "Pr(>|t|)"],
      n             = nobs(ivm)
    )
  })
}

# Run
iv_results_hybrid <- expand.grid(
  variable = narratives,
  lag      = 1:12,
  stringsAsFactors = FALSE
) %>%
  purrr::pmap_dfr(~ run_iv_lag_hybrid(..1, ..2))

iv_hits_hybrid <- iv_results_hybrid %>%
  filter(F_first_stage > 10, p_value < 0.1) %>%
  arrange(desc(F_first_stage), p_value)

iv_hits_hybrid
```

Explaining the electoral comp code below:

What I did with the electoral competition adjustment was to construct a separate country–month panel of political competition using the CLEA election data, and then merge that into my main dataset so I could test whether the effect of narratives on public attention depends on the electoral environment.

I started by loading the two CLEA datasets, parliamentary_elections_v2.dta and presidential_elections_v2.dta, into parl_raw and pres_raw. Because different countries have different institutional structures, I created a country_map that assigns each country an election type through the system variable—either "parliamentary" or "presidential". This determines whether I use seat shares or vote shares to measure competition.

For parliamentary systems, I reshaped the data using pivot_longer() on variables like party_1, seat_share_1, etc., and constructed a dataset where each row corresponds to a party within an election. I then ranked parties by seat_share, kept the top two, and computed the electoral margin as margin_pp = abs(top1_share - top2_share). For presidential systems, I followed the same logic but used vote_share1 and vote_share2, defining final_share as the second-round vote share when available, and otherwise the first round. Again, I ranked candidates, kept the top two, and computed margin_pp.

I then combined these into a single dataset called election_margins, which contains iso2, election_date, top1_share, top2_share, and margin_pp. This gives me an election-level measure of political competition across all countries.

Next, I constructed a full country–month panel called monthly_panel using expand_grid() over all countries in target_iso2 and all months in target_months. I merged the election data into this panel in two ways. First, I created last_election_panel, which assigns to each iso2–month_date pair the most recent election that occurred before that month. This gives me variables like last_election_date, last_election_margin_pp, and the identities and shares of the top two competitors. Second, I created next_election_panel, which assigns the next upcoming election date, stored in next_election_date.

I then merged these together into a dataset called competition_merge_ready. From this, I constructed several key variables that I use in the regressions. The main continuous measure is last_election_margin_pp, which captures how competitive the most recent election was. I also created binary indicators like close_race_5pp and close_race_10pp, which equal 1 if the last election margin is below 5 or 10 percentage points. To capture timing, I constructed months_since_last_election and months_to_next_election, and an indicator election_month for whether a given month coincides with an election.

After merging this dataset into my main panel df_base_levels_m, I created additional derived variables used in the regressions. In particular, I defined near_election_12m and near_election_6m as indicators for whether months_to_next_election is less than or equal to 12 or 6 months. I also created a continuous measure of competition, high_competition_cont, defined as -last_election_margin_pp, so that higher values correspond to more competitive environments.

In the regressions, I kept my baseline specification in differences. That means my dependent variable is dG = G_Trends - lag(G_Trends), and my main explanatory variable is p_lag, which is the lagged change in a narrative variable, constructed as dN = Narrative - lag(Narrative) and then p_lag = lag(dN, L).

To incorporate electoral competition, I estimated models where I interact p_lag with the competition variables. For example, in run_lags_diff_close_race, I estimate:

dG ~ p_lag * close_race_5pp + internet + gini_disp | country^year

Here, coef_p_lag captures the effect of narrative changes when close_race_5pp = 0, and coef_inter on p_lag:close_race_5pp captures how that effect changes when the last election was a close race. I run an analogous specification using near_election_12m in run_lags_diff_near_election, and a continuous version using last_election_margin_pp in run_lags_diff_margin.

To interpret these properly, I also constructed comparison tables like compare_near_election, compare_close_race, and compare_margin. These combine the interaction results with baseline estimates so I can compute quantities like effect_non_election = coef_p_lag and effect_near_election = coef_p_lag + coef_inter. In the continuous case, I evaluate the effect at different levels of competition using expressions like coef_p_lag + coef_inter * 5.

```{r}
# =========================
# Build monthly political-competition panel
# from CLEA parliamentary + presidential .dta files
# =========================

# -------------------------
# File paths
# -------------------------
parl_raw <- read_dta("parliamentary_elections_v2.dta")
pres_raw <- read_dta("presidential_elections_v2.dta")

# -------------------------
# Your panel countries and months
# -------------------------
target_iso2 <- c("AU","BD","CA","GB","GH","HK","IE","IN","JM","KE",
                 "LK","MY","NG","NZ","PH","PK","SG","TZ","US","ZA")

target_months <- seq(as.Date("2011-01-01"), as.Date("2024-12-01"), by = "month")

# -------------------------
# Country mapping + system choice
# (the election that determines executive power)
# -------------------------
country_map <- tibble::tribble(
  ~iso2, ~country_name,    ~system,
  "AU",  "Australia",      "parliamentary",
  "BD",  "Bangladesh",     "parliamentary",
  "CA",  "Canada",         "parliamentary",
  "GB",  "UK",             "parliamentary",
  "GH",  "Ghana",          "presidential",
  "HK",  NA_character_,    "none",
  "IE",  "Ireland",        "parliamentary",
  "IN",  "India",          "parliamentary",
  "JM",  "Jamaica",        "parliamentary",
  "KE",  "Kenya",          "presidential",
  "LK",  "Sri Lanka",      "presidential",
  "MY",  "Malaysia",       "parliamentary",
  "NG",  "Nigeria",        "presidential",
  "NZ",  "New Zealand",    "parliamentary",
  "PH",  "Philippines",    "presidential",
  "PK",  "Pakistan",       "parliamentary",
  "SG",  "Singapore",      "parliamentary",
  "TZ",  "Tanzania",       "presidential",
  "US",  "USA",            "presidential",
  "ZA",  "S. Africa",      "parliamentary"
)


# -------------------------
# Helper: robust election date
# -------------------------
make_election_date <- function(date_col, year_col, month_col = NULL) {
  # Use exact date if available; otherwise fall back to year-month if month exists; else June of year
  out <- suppressWarnings(as.Date(date_col))
  if (!is.null(month_col)) {
    fallback <- as.Date(sprintf("%s-%02d-01", year_col, ifelse(is.na(month_col), 6, as.integer(month_col))))
  } else {
    fallback <- as.Date(sprintf("%s-06-01", year_col))
  }
  ifelse(is.na(out), fallback, out) |> as.Date(origin = "1970-01-01")
}

# -------------------------
# Parliamentary systems:
# use TOP-TWO SEAT SHARE margin
# -------------------------
parl_keep <- country_map %>%
  filter(system == "parliamentary") %>%
  pull(country_name)

parl_elections <- parl_raw %>%
  filter(country %in% parl_keep) %>%
  mutate(
    election_id = row_number(),
    election_date = make_election_date(date, year, month)
  ) %>%
  select(election_id, country, year, election_date, matches("^(party|seat_share)_[0-9]+$")) %>%
  pivot_longer(
    cols = matches("^(party|seat_share)_[0-9]+$"),
    names_to = c(".value", "slot"),
    names_pattern = "^(party|seat_share)_([0-9]+)$"
  ) %>%
  mutate(
    slot = as.integer(slot),
    seat_share = suppressWarnings(as.numeric(seat_share))
  ) %>%
  filter(!is.na(seat_share), seat_share > 0) %>%
  group_by(election_id, country, year, election_date) %>%
  arrange(desc(seat_share), .by_group = TRUE) %>%
  mutate(rank = row_number()) %>%
  filter(rank <= 2) %>%
  summarise(
    top1_name = party[rank == 1][1],
    top1_share = seat_share[rank == 1][1],
    top2_name = party[rank == 2][1],
    top2_share = seat_share[rank == 2][1],
    margin_pp = abs(top1_share - top2_share),
    metric_used = "seat_share",
    .groups = "drop"
  ) %>%
  left_join(country_map %>% select(iso2, country_name), by = c("country" = "country_name")) %>%
  select(iso2, country, election_date, year, top1_name, top1_share, top2_name, top2_share, margin_pp, metric_used)

# -------------------------
# Presidential systems:
# use TOP-TWO VOTE SHARE margin
# Prefer round 2 if available; otherwise use round 1
# -------------------------
pres_keep <- country_map %>%
  filter(system == "presidential") %>%
  pull(country_name)

pres_elections <- pres_raw %>%
  filter(country %in% pres_keep) %>%
  mutate(
    election_id = row_number(),
    election_date = make_election_date(date, year, month)
  ) %>%
  select(election_id, country, year, election_date, matches("^(candidate|party|vote_share1|vote_share2)_[0-9]+$")) %>%
  pivot_longer(
    cols = matches("^(candidate|party|vote_share1|vote_share2)_[0-9]+$"),
    names_to = c(".value", "slot"),
    names_pattern = "^(candidate|party|vote_share1|vote_share2)_([0-9]+)$"
  ) %>%
  mutate(
    slot = as.integer(slot),
    vote_share1 = suppressWarnings(as.numeric(vote_share1)),
    vote_share2 = suppressWarnings(as.numeric(vote_share2)),
    final_share = ifelse(!is.na(vote_share2), vote_share2, vote_share1),
    label = dplyr::coalesce(candidate, party)
  ) %>%
  filter(!is.na(final_share), final_share > 0) %>%
  group_by(election_id, country, year, election_date) %>%
  arrange(desc(final_share), .by_group = TRUE) %>%
  mutate(rank = row_number()) %>%
  filter(rank <= 2) %>%
  summarise(
    top1_name = label[rank == 1][1],
    top1_share = final_share[rank == 1][1],
    top2_name = label[rank == 2][1],
    top2_share = final_share[rank == 2][1],
    margin_pp = abs(top1_share - top2_share),
    metric_used = ifelse(any(!is.na(vote_share2)), "vote_share_round2_if_available_else_round1", "vote_share_round1"),
    .groups = "drop"
  ) %>%
  left_join(country_map %>% select(iso2, country_name), by = c("country" = "country_name")) %>%
  select(iso2, country, election_date, year, top1_name, top1_share, top2_name, top2_share, margin_pp, metric_used)

# -------------------------
# Combine election-level margins
# -------------------------
election_margins <- bind_rows(parl_elections, pres_elections) %>%
  distinct(iso2, election_date, .keep_all = TRUE) %>%
  arrange(iso2, election_date)

# -------------------------
# Build full monthly panel for all 20 countries
# -------------------------
monthly_panel <- tidyr::expand_grid(
  iso2 = target_iso2,
  month_date = target_months
)

# -------------------------
# Last election carried forward
# -------------------------
last_election_panel <- monthly_panel %>%
  left_join(election_margins, by = "iso2") %>%
  filter(is.na(election_date) | election_date <= month_date) %>%
  group_by(iso2, month_date) %>%
  slice_max(order_by = election_date, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    iso2,
    month_date,
    last_election_date = election_date,
    last_election_year = year,
    last_top1_name = top1_name,
    last_top1_share = top1_share,
    last_top2_name = top2_name,
    last_top2_share = top2_share,
    last_election_margin_pp = margin_pp,
    metric_used
  )

# -------------------------
# Next election lookup
# -------------------------
next_election_panel <- monthly_panel %>%
  left_join(election_margins %>% select(iso2, election_date), by = "iso2") %>%
  filter(is.na(election_date) | election_date >= month_date) %>%
  group_by(iso2, month_date) %>%
  slice_min(order_by = election_date, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    iso2,
    month_date,
    next_election_date = election_date
  )

# -------------------------
# Merge together and create competition variables
# -------------------------
competition_merge_ready <- monthly_panel %>%
  left_join(last_election_panel, by = c("iso2", "month_date")) %>%
  left_join(next_election_panel, by = c("iso2", "month_date")) %>%
  left_join(country_map %>% select(iso2, system), by = "iso2") %>%
  mutate(
    months_since_last_election = ifelse(
      !is.na(last_election_date),
      12 * (year(month_date) - year(last_election_date)) + (month(month_date) - month(last_election_date)),
      NA_real_
    ),
    months_to_next_election = ifelse(
      !is.na(next_election_date),
      12 * (year(next_election_date) - year(month_date)) + (month(next_election_date) - month(month_date)),
      NA_real_
    ),
    election_month = ifelse(!is.na(last_election_date) & floor_date(month_date, "month") == floor_date(last_election_date, "month"), 1L, 0L),
    close_race_5pp = ifelse(!is.na(last_election_margin_pp) & last_election_margin_pp < 5, 1L, 0L),
    close_race_10pp = ifelse(!is.na(last_election_margin_pp) & last_election_margin_pp < 10, 1L, 0L),
    month = format(month_date, "%Y-%m")
  ) %>%
  select(
    iso2,
    month,
    system,
    metric_used,
    last_election_date,
    next_election_date,
    months_since_last_election,
    months_to_next_election,
    election_month,
    last_top1_name,
    last_top1_share,
    last_top2_name,
    last_top2_share,
    last_election_margin_pp,
    close_race_5pp,
    close_race_10pp
  ) %>%
  arrange(iso2, month)

write.csv(competition_merge_ready, "competition_merge_ready_2011_2024.csv", row.names = FALSE)
```

```{r}
# Merge electoral comp vars in
df_base_levels_m <- df_base_levels_m %>%
  left_join(
    competition_merge_ready %>%
      rename(country = iso2, year_month = month),
    by = c("country", "year_month")
  )

df_base_levels_m <- df_base_levels_m %>%
  mutate(
    close_race_5pp = as.numeric(close_race_5pp),
    close_race_10pp = as.numeric(close_race_10pp),
    election_month = as.numeric(election_month),

    near_election_12m = ifelse(!is.na(months_to_next_election) & months_to_next_election <= 12, 1, 0),
    near_election_6m  = ifelse(!is.na(months_to_next_election) & months_to_next_election <= 6, 1, 0),

    high_competition_cont = ifelse(!is.na(last_election_margin_pp), -last_election_margin_pp, NA_real_)
  )
```

```{r}
# Reduced form with close race var
run_lags_diff_close_race <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(close_race_5pp),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag * close_race_5pp + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable = var,
      lag      = L,
      coef_p_lag = ct["p_lag", "Estimate"],
      p_p_lag    = ct["p_lag", "Pr(>|t|)"],
      coef_inter = ct["p_lag:close_race_5pp", "Estimate"],
      p_inter    = ct["p_lag:close_race_5pp", "Pr(>|t|)"],
      n        = nobs(m),
      spec     = "diff_rf_close_race"
    )
  })
}

results_close_race <- purrr::map_dfr(narratives, run_lags_diff_close_race)

close_race_hits <- results_close_race %>%
  filter(p_inter < 0.1) %>%
  arrange(p_inter)

close_race_hits
```

```{r}
# -------------------------
#  Same idea, but using "near election" instead of close race
# -------------------------

run_lags_diff_near_election <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(near_election_12m),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag * near_election_12m + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable   = var,
      lag        = L,
      coef_p_lag = ct["p_lag", "Estimate"],
      p_p_lag    = ct["p_lag", "Pr(>|t|)"],
      coef_inter = ct["p_lag:near_election_12m", "Estimate"],
      p_inter    = ct["p_lag:near_election_12m", "Pr(>|t|)"],
      n          = nobs(m),
      spec       = "diff_rf_near_election"
    )
  })
}

results_near_election <- purrr::map_dfr(narratives, run_lags_diff_near_election)

near_election_hits <- results_near_election %>%
  filter(p_inter < 0.1) %>%
  arrange(p_inter)

near_election_hits
```

```{r}
# -------------------------
# Continuous version: smaller margin = more competitive
# -------------------------

run_lags_diff_margin <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(last_election_margin_pp),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag * last_election_margin_pp + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable   = var,
      lag        = L,
      coef_p_lag = ct["p_lag", "Estimate"],
      p_p_lag    = ct["p_lag", "Pr(>|t|)"],
      coef_inter = ct["p_lag:last_election_margin_pp", "Estimate"],
      p_inter    = ct["p_lag:last_election_margin_pp", "Pr(>|t|)"],
      n          = nobs(m),
      spec       = "diff_rf_margin"
    )
  })
}

results_margin <- purrr::map_dfr(narratives, run_lags_diff_margin)

margin_hits <- results_margin %>%
  filter(p_inter < 0.1) %>%
  arrange(p_inter)

margin_hits
```

```{r}
# -------------------------
# Combine all election-heterogeneity results
# -------------------------

interaction_results <- bind_rows(
  results_close_race,
  results_near_election,
  results_margin
)

interaction_hits <- interaction_results %>%
  filter(p_inter < 0.1) %>%
  arrange(spec, p_inter)

interaction_hits
```

```{r}
# -------------------------
# Sample checks
# -------------------------

# How many countries have election competition data?
df_base_levels_m %>%
  summarise(
    n_obs = n(),
    n_close_race_nonmissing = sum(!is.na(close_race_5pp)),
    n_margin_nonmissing = sum(!is.na(last_election_margin_pp)),
    n_near_election_nonmissing = sum(!is.na(near_election_12m))
  )

# By country
df_base_levels_m %>%
  group_by(country) %>%
  summarise(
    n_obs = n(),
    n_close_race_nonmissing = sum(!is.na(close_race_5pp)),
    n_margin_nonmissing = sum(!is.na(last_election_margin_pp))
  ) %>%
  arrange(country)
```


```{r}
# -------------------------
# Baseline on same sample as close-race regression
# -------------------------

run_lags_diff_m_close_sample <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(close_race_5pp),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable = var,
      lag      = L,
      coef     = ct["p_lag", "Estimate"],
      p_value  = ct["p_lag", "Pr(>|t|)"],
      n        = nobs(m),
      spec     = "baseline_close_race_sample"
    )
  })
}

baseline_close_sample <- purrr::map_dfr(narratives, run_lags_diff_m_close_sample)

baseline_close_sample %>%
  filter(p_value < 0.1) %>%
  arrange(p_value)

run_lags_diff_m_near_election_sample <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(near_election_12m),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable = var,
      lag      = L,
      coef     = ct["p_lag", "Estimate"],
      p_value  = ct["p_lag", "Pr(>|t|)"],
      n        = nobs(m),
      spec     = "baseline_near_election_sample"
    )
  })
}

baseline_near_election_sample <- purrr::map_dfr(narratives, run_lags_diff_m_near_election_sample)

run_lags_diff_m_margin_sample <- function(var, L_max = 12){

  map_dfr(1:L_max, function(L){

    d <- df_base_levels_m %>%
      arrange(country, year_month) %>%
      group_by(country) %>%
      mutate(
        dG    = G_Trends - lag(G_Trends),
        dN    = .data[[var]] - lag(.data[[var]]),
        p_lag = lag(dN, L)
      ) %>%
      ungroup() %>%
      filter(
        !is.na(dG),
        !is.na(p_lag),
        !is.na(last_election_margin_pp),
        !is.na(internet),
        !is.na(gini_disp)
      )

    m <- feols(
      dG ~ p_lag + internet + gini_disp | country^year,
      data = d,
      cluster = ~country
    )

    ct <- summary(m)$coeftable

    tibble(
      variable = var,
      lag      = L,
      coef     = ct["p_lag", "Estimate"],
      p_value  = ct["p_lag", "Pr(>|t|)"],
      n        = nobs(m),
      spec     = "baseline_margin_sample"
    )
  })
}

baseline_margin_sample <- purrr::map_dfr(narratives, run_lags_diff_m_margin_sample)
```

```{r}
compare_near_election <- results_near_election %>%
  left_join(
    all_lags_diff_m %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_non_election = coef_p_lag,
    effect_near_election = coef_p_lag + coef_inter
  )

compare_close_race <- results_close_race %>%
  left_join(
    baseline_close_sample %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_non_close = coef_p_lag,
    effect_close_race = coef_p_lag + coef_inter
  )

compare_margin <- results_margin %>%
  left_join(
    baseline_margin_sample %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_high_competition = coef_p_lag + coef_inter * 5,
    effect_medium_competition = coef_p_lag + coef_inter * 10,
    effect_low_competition = coef_p_lag + coef_inter * 20
  )
```

```{r}
# -------------------------
# Load text-level narrative counts
# -------------------------

texts_raw <- read_csv("PerArticle_REBUILT.csv", show_col_types = FALSE) %>%
  mutate(
    country = toupper(country),
    month   = as.character(month)
  ) %>%
  filter(
    !is.na(domain),
    !is.na(country),
    !is.na(month),
    !is.na(total_sentences),
    total_sentences > 0
  )

# -------------------------
# Aggregate to domain x country x month
# narrative cols are already sentence counts
# -------------------------

domain_month_counts <- texts_raw %>%
  group_by(domain, country, month) %>%
  summarise(
    total_sentences = sum(total_sentences, na.rm = TRUE),

    Restrictive_redistribution_sent =
      sum(Restrictive_redistribution, na.rm = TRUE),
    Restrictive_meritocracy_sent =
      sum(Restrictive_meritocracy, na.rm = TRUE),
    Restrictive_equal_opportunities_sent =
      sum(Restrictive_equal_opportunities, na.rm = TRUE),
    Restrictive_fairness_sent =
      sum(Restrictive_fairness, na.rm = TRUE),

    Permissive_redistribution_sent =
      sum(Permissive_redistribution, na.rm = TRUE),
    Permissive_meritocracy_sent =
      sum(Permissive_meritocracy, na.rm = TRUE),
    Permissive_equal_opportunities_sent =
      sum(Permissive_equal_opportunities, na.rm = TRUE),
    Permissive_fairness_sent =
      sum(Permissive_fairness, na.rm = TRUE),

    .groups = "drop"
  ) %>%
  filter(total_sentences > 0)

# -------------------------
# helper to parse site visits
# -------------------------

parse_site_visits <- function(x) {
  x <- tolower(trimws(as.character(x)))
  x <- ifelse(x %in% c("", "na", "n/a", "null", "none"), NA, x)
  x_clean <- gsub(",", "", x)

  out <- rep(NA_real_, length(x_clean))

  million_idx <- grepl("million", x_clean)
  if(any(million_idx, na.rm = TRUE)){
    nums <- suppressWarnings(as.numeric(gsub("\\s*million.*$", "", x_clean[million_idx])))
    out[million_idx] <- nums * 1e6
  }

  plain_idx <- !million_idx & !is.na(x_clean)
  if(any(plain_idx, na.rm = TRUE)){
    out[plain_idx] <- suppressWarnings(as.numeric(x_clean[plain_idx]))
  }

  out
}

# -------------------------
# read all top domain files for readership + ownership
# -------------------------

readership_dir <- "Readership"
top_domain_files <- list.files(
  path = readership_dir,
  pattern = "^[A-Za-z0-9]+_top_domains_for_labeling\\.csv$",
  full.names = TRUE
)

owner_readership_raw <- map_dfr(top_domain_files, function(f){

  file_name <- basename(f)
  country_code <- toupper(str_extract(file_name, "^[A-Za-z0-9]+"))

  df <- read_csv(f, show_col_types = FALSE)

  names(df) <- names(df) %>%
    str_trim() %>%
    str_replace_all("\\s+", "_") %>%
    str_replace_all("[()]", "") %>%
    str_replace_all("/", "_") %>%
    str_replace_all("-", "_")

  domain_col <- names(df)[names(df) %in% c("domain", "adjudomain")]
  if(length(domain_col) == 0) stop("No domain/adjudomain column in ", file_name)
  domain_col <- domain_col[1]

  owner_col <- names(df)[names(df) == "owner_group"]
  if(length(owner_col) == 0) stop("No owner_group column in ", file_name)
  owner_col <- owner_col[1]

  visit_col <- names(df)[str_detect(names(df), "^site_visits")]
  if(length(visit_col) == 0) stop("No site visits column in ", file_name)
  visit_col <- visit_col[1]

  df %>%
    transmute(
      country = country_code,
      domain = as.character(.data[[domain_col]]),
      owner_group = as.character(.data[[owner_col]]),
      site_visits_raw = .data[[visit_col]],
      site_visits = parse_site_visits(.data[[visit_col]])
    )
})

owner_readership <- owner_readership_raw %>%
  mutate(
    country = toupper(country),
    domain = as.character(domain),
    owner_group = ifelse(
      is.na(owner_group) | trimws(owner_group) == "",
      paste0("UNKNOWN_OWNER__", domain),
      owner_group
    )
  ) %>%
  filter(!is.na(domain), !is.na(site_visits), site_visits > 0) %>%
  group_by(country) %>%
  mutate(
    readership_weight = site_visits / sum(site_visits, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  distinct(country, domain, .keep_all = TRUE)

# -------------------------
# Load domain-level article counts
# domain_counts.csv columns: year_month, country, domain, count
# -------------------------

domain_article_counts <- read_csv("domain_counts.csv", show_col_types = FALSE) %>%
  mutate(
    country = toupper(country),
    month   = as.character(year_month),
    domain  = as.character(domain),
    article_count = as.numeric(count)
  ) %>%
  select(country, month, domain, article_count) %>%
  filter(!is.na(article_count), article_count > 0)

# -------------------------
# Merge readership + article counts into domain-month data
# -------------------------

domain_month_weighted_input <- domain_month_counts %>%
  left_join(
    owner_readership %>%
      select(country, domain, owner_group, site_visits, readership_weight),
    by = c("country", "domain")
  ) %>%
  left_join(
    domain_article_counts,
    by = c("country", "domain", "month")
  )

# Coverage checks
coverage_summary <- domain_month_weighted_input %>%
  group_by(country) %>%
  summarise(
    outlet_month_rows = n(),
    readership_matched = sum(!is.na(readership_weight)),
    article_count_matched = sum(!is.na(article_count)),
    both_matched = sum(!is.na(readership_weight) & !is.na(article_count)),
    .groups = "drop"
  )

print(coverage_summary, n = Inf)

# For baseline weighting: need readership
domain_month_weighted_input_baseline <- domain_month_weighted_input %>%
  filter(!is.na(readership_weight), readership_weight > 0)

# For discounted version: need readership + article_count
domain_month_weighted_input_disc <- domain_month_weighted_input %>%
  filter(
    !is.na(readership_weight), readership_weight > 0,
    !is.na(article_count), article_count > 0
  )

# -------------------------
# Baseline weighted narratives
# -------------------------

weighted_country_month_baseline <- domain_month_weighted_input_baseline %>%
  group_by(country, month) %>%
  summarise(
    Restrictive_redistribution_w =
      sum(readership_weight * Restrictive_redistribution_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Restrictive_meritocracy_w =
      sum(readership_weight * Restrictive_meritocracy_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Restrictive_equal_opportunities_w =
      sum(readership_weight * Restrictive_equal_opportunities_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Restrictive_fairness_w =
      sum(readership_weight * Restrictive_fairness_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Permissive_redistribution_w =
      sum(readership_weight * Permissive_redistribution_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Permissive_meritocracy_w =
      sum(readership_weight * Permissive_meritocracy_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Permissive_equal_opportunities_w =
      sum(readership_weight * Permissive_equal_opportunities_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    Permissive_fairness_w =
      sum(readership_weight * Permissive_fairness_sent, na.rm = TRUE) /
      sum(readership_weight * total_sentences, na.rm = TRUE),

    weighted_total_sentences_baseline =
      sum(readership_weight * total_sentences, na.rm = TRUE),

    outlets_used = n(),
    .groups = "drop"
  )

# -------------------------
# Discounted version using article counts
# effective weight = readership_weight / article_count
# -------------------------

domain_month_weighted_input_disc <- domain_month_weighted_input_disc %>%
  mutate(
    readership_weight_per_article = readership_weight / article_count
  )

weighted_country_month_discounted <- domain_month_weighted_input_disc %>%
  group_by(country, month) %>%
  summarise(
    Restrictive_redistribution_w_disc =
      sum(readership_weight_per_article * Restrictive_redistribution_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Restrictive_meritocracy_w_disc =
      sum(readership_weight_per_article * Restrictive_meritocracy_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Restrictive_equal_opportunities_w_disc =
      sum(readership_weight_per_article * Restrictive_equal_opportunities_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Restrictive_fairness_w_disc =
      sum(readership_weight_per_article * Restrictive_fairness_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Permissive_redistribution_w_disc =
      sum(readership_weight_per_article * Permissive_redistribution_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Permissive_meritocracy_w_disc =
      sum(readership_weight_per_article * Permissive_meritocracy_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Permissive_equal_opportunities_w_disc =
      sum(readership_weight_per_article * Permissive_equal_opportunities_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    Permissive_fairness_w_disc =
      sum(readership_weight_per_article * Permissive_fairness_sent, na.rm = TRUE) /
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    weighted_total_sentences_discounted =
      sum(readership_weight_per_article * total_sentences, na.rm = TRUE),

    outlets_used = n(),
    .groups = "drop"
  )

# -------------------------
# Owner-level concentration using article-adjusted exposure
# -------------------------

domain_month_owner_input <- domain_month_weighted_input_disc %>%
  mutate(
    exposure_mass_owner = readership_weight_per_article * total_sentences
  )

owner_month_mass <- domain_month_owner_input %>%
  group_by(country, month, owner_group) %>%
  summarise(
    owner_exposure_mass = sum(exposure_mass_owner, na.rm = TRUE),
    owner_total_sentences = sum(total_sentences, na.rm = TRUE),
    outlets_in_owner = n_distinct(domain),
    .groups = "drop"
  )

owner_month_shares <- owner_month_mass %>%
  group_by(country, month) %>%
  mutate(
    total_exposure_mass_country_month = sum(owner_exposure_mass, na.rm = TRUE),
    owner_share = owner_exposure_mass / total_exposure_mass_country_month
  ) %>%
  ungroup()

owner_concentration_monthly <- owner_month_shares %>%
  arrange(country, month, desc(owner_share)) %>%
  group_by(country, month) %>%
  mutate(rank = row_number()) %>%
  summarise(
    HHI_owner_w = sum(owner_share^2, na.rm = TRUE),
    ENP_owner_w = ifelse(sum(owner_share^2, na.rm = TRUE) > 0,
                         1 / sum(owner_share^2, na.rm = TRUE),
                         NA_real_),
    Top1_owner_w = sum(owner_share[rank <= 1], na.rm = TRUE),
    Top3_owner_w = sum(owner_share[rank <= 3], na.rm = TRUE),
    Top5_owner_w = sum(owner_share[rank <= 5], na.rm = TRUE),
    Entropy_owner_w = -sum(ifelse(owner_share > 0, owner_share * log(owner_share), 0), na.rm = TRUE),
    TailShare_owner_w = sum(owner_share[rank > 5], na.rm = TRUE),
    owners_used = n(),
    .groups = "drop"
  )

# -------------------------
# Merge back into main panel
# -------------------------

df_base_levels_m_w_baseline <- df_base_levels_m %>%
  left_join(
    weighted_country_month_baseline %>% rename(year_month = month),
    by = c("country", "year_month")
  ) %>%
  mutate(
    Restrictive_equal_opportunities_rate_w =
      ifelse(!is.na(Restrictive_equal_opportunities_w),
             Restrictive_equal_opportunities_w,
             Restrictive_equal_opportunities_rate),
    Restrictive_fairness_rate_w =
      ifelse(!is.na(Restrictive_fairness_w),
             Restrictive_fairness_w,
             Restrictive_fairness_rate),
    Restrictive_meritocracy_rate_w =
      ifelse(!is.na(Restrictive_meritocracy_w),
             Restrictive_meritocracy_w,
             Restrictive_meritocracy_rate),
    Restrictive_redistribution_rate_w =
      ifelse(!is.na(Restrictive_redistribution_w),
             Restrictive_redistribution_w,
             Restrictive_redistribution_rate),

    Permissive_equal_opportunities_rate_w =
      ifelse(!is.na(Permissive_equal_opportunities_w),
             Permissive_equal_opportunities_w,
             Permissive_equal_opportunities_rate),
    Permissive_fairness_rate_w =
      ifelse(!is.na(Permissive_fairness_w),
             Permissive_fairness_w,
             Permissive_fairness_rate),
    Permissive_meritocracy_rate_w =
      ifelse(!is.na(Permissive_meritocracy_w),
             Permissive_meritocracy_w,
             Permissive_meritocracy_rate),
    Permissive_redistribution_rate_w =
      ifelse(!is.na(Permissive_redistribution_w),
             Permissive_redistribution_w,
             Permissive_redistribution_rate)
  )

df_base_levels_m_w_discounted <- df_base_levels_m %>%
  left_join(
    weighted_country_month_discounted %>% rename(year_month = month),
    by = c("country", "year_month")
  ) %>%
  mutate(
    Restrictive_equal_opportunities_rate_w_disc =
      ifelse(!is.na(Restrictive_equal_opportunities_w_disc),
             Restrictive_equal_opportunities_w_disc,
             Restrictive_equal_opportunities_rate),
    Restrictive_fairness_rate_w_disc =
      ifelse(!is.na(Restrictive_fairness_w_disc),
             Restrictive_fairness_w_disc,
             Restrictive_fairness_rate),
    Restrictive_meritocracy_rate_w_disc =
      ifelse(!is.na(Restrictive_meritocracy_w_disc),
             Restrictive_meritocracy_w_disc,
             Restrictive_meritocracy_rate),
    Restrictive_redistribution_rate_w_disc =
      ifelse(!is.na(Restrictive_redistribution_w_disc),
             Restrictive_redistribution_w_disc,
             Restrictive_redistribution_rate),

    Permissive_equal_opportunities_rate_w_disc =
      ifelse(!is.na(Permissive_equal_opportunities_w_disc),
             Permissive_equal_opportunities_w_disc,
             Permissive_equal_opportunities_rate),
    Permissive_fairness_rate_w_disc =
      ifelse(!is.na(Permissive_fairness_w_disc),
             Permissive_fairness_w_disc,
             Permissive_fairness_rate),
    Permissive_meritocracy_rate_w_disc =
      ifelse(!is.na(Permissive_meritocracy_w_disc),
             Permissive_meritocracy_w_disc,
             Permissive_meritocracy_rate),
    Permissive_redistribution_rate_w_disc =
      ifelse(!is.na(Permissive_redistribution_w_disc),
             Permissive_redistribution_w_disc,
             Permissive_redistribution_rate)
  )

df_base_levels_m_owner_w <- df_base_levels_m %>%
  left_join(
    owner_concentration_monthly %>% rename(year_month = month),
    by = c("country", "year_month")
  )

write_csv(weighted_country_month_baseline, "weighted_country_month_baseline.csv")
write_csv(weighted_country_month_discounted, "weighted_country_month_discounted.csv")
write_csv(owner_concentration_monthly, "owner_concentration_monthly.csv")
```

```{r}
# -------------------------
# Build final regression panels
# -------------------------

# Baseline narratives + owner IVs
df_weighted_owner_baseline <- df_base_levels_m_w_baseline %>%
  left_join(
    owner_concentration_monthly %>%
      rename(year_month = month),
    by = c("country", "year_month")
  )

# Discounted narratives + owner IVs
df_weighted_owner_discounted <- df_base_levels_m_w_discounted %>%
  left_join(
    owner_concentration_monthly %>%
      rename(year_month = month),
    by = c("country", "year_month")
  )

# -------------------------
# Variable lists
# -------------------------

weighted_narratives_baseline <- c(
  "Restrictive_equal_opportunities_rate_w",
  "Restrictive_fairness_rate_w",
  "Restrictive_meritocracy_rate_w",
  "Restrictive_redistribution_rate_w",
  "Permissive_equal_opportunities_rate_w",
  "Permissive_fairness_rate_w",
  "Permissive_meritocracy_rate_w",
  "Permissive_redistribution_rate_w"
)

weighted_narratives_discounted <- c(
  "Restrictive_equal_opportunities_rate_w_disc",
  "Restrictive_fairness_rate_w_disc",
  "Restrictive_meritocracy_rate_w_disc",
  "Restrictive_redistribution_rate_w_disc",
  "Permissive_equal_opportunities_rate_w_disc",
  "Permissive_fairness_rate_w_disc",
  "Permissive_meritocracy_rate_w_disc",
  "Permissive_redistribution_rate_w_disc"
)

owner_iv_vars <- c(
  "HHI_owner_w",
  "ENP_owner_w",
  "Top1_owner_w",
  "Top3_owner_w",
  "Top5_owner_w",
  "Entropy_owner_w",
  "TailShare_owner_w"
)

# -------------------------
# Helper: label fn
# -------------------------

label_results <- function(df, variable_col = "variable") {
  df %>%
    mutate(
      narrative = case_when(
        grepl("equal_opportunities", .data[[variable_col]]) ~ "equal_opportunities",
        grepl("fairness", .data[[variable_col]]) ~ "fairness",
        grepl("meritocracy", .data[[variable_col]]) ~ "meritocracy",
        grepl("redistribution", .data[[variable_col]]) ~ "redistribution"
      ),
      type = case_when(
        grepl("Restrictive", .data[[variable_col]]) ~ "restrictive",
        grepl("Permissive", .data[[variable_col]]) ~ "permissive"
      )
    )
}

# -------------------------
# Narrative OLS
# dG on lagged dN
# -------------------------

run_narrative_ols_safe <- function(data_panel, variable, lag){

  d <- data_panel %>%
    arrange(country, year_month) %>%
    group_by(country) %>%
    mutate(
      dG    = G_Trends - lag(G_Trends),
      dN    = .data[[variable]] - lag(.data[[variable]]),
      p_lag = lag(dN, lag)
    ) %>%
    ungroup() %>%
    filter(
      !is.na(dG),
      !is.na(p_lag)
    )

  if(nrow(d) < 30){
    return(tibble(
      variable = variable,
      lag = lag,
      coef = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "too_few_obs"
    ))
  }

  m <- tryCatch(
    feols(
      dG ~ p_lag | country^year,
      data = d,
      cluster = ~country
    ),
    error = function(e) NULL
  )

  if(is.null(m)){
    return(tibble(
      variable = variable,
      lag = lag,
      coef = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "failed"
    ))
  }

  ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

  if(is.null(ct) || !("p_lag" %in% rownames(ct))){
    return(tibble(
      variable = variable,
      lag = lag,
      coef = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "no_coef"
    ))
  }

  tibble(
    variable = variable,
    lag = lag,
    coef = ct["p_lag", "Estimate"],
    p_value = ct["p_lag", "Pr(>|t|)"],
    n = nrow(d),
    status = "ok"
  )
}

# -------------------------
# Baseline weighted narrative OLS
# -------------------------

narrative_ols_baseline <- expand.grid(
  variable = weighted_narratives_baseline,
  lag = 1:12,
  stringsAsFactors = FALSE
) %>%
  pmap_dfr(~ run_narrative_ols_safe(df_weighted_owner_baseline, ..1, ..2))

narrative_ols_baseline_hits <- narrative_ols_baseline %>%
  filter(status == "ok", p_value < 0.1) %>%
  label_results() %>%
  mutate(
    coef = round(coef, 3),
    p_value = round(p_value, 3)
  ) %>%
  select(narrative, type, lag, coef, p_value, n) %>%
  arrange(p_value)

narrative_ols_baseline_hits

# -------------------------
# Discounted weighted narrative OLS
# -------------------------

narrative_ols_discounted <- expand.grid(
  variable = weighted_narratives_discounted,
  lag = 1:12,
  stringsAsFactors = FALSE
) %>%
  pmap_dfr(~ run_narrative_ols_safe(df_weighted_owner_discounted, ..1, ..2))

narrative_ols_discounted_hits <- narrative_ols_discounted %>%
  filter(status == "ok", p_value < 0.1) %>%
  label_results() %>%
  mutate(
    coef = round(coef, 3),
    p_value = round(p_value, 3)
  ) %>%
  select(narrative, type, lag, coef, p_value, n) %>%
  arrange(p_value)

narrative_ols_discounted_hits

# -------------------------
# Reduced form
# dG on lagged dIV
# -------------------------

run_rf_safe <- function(data_panel, iv, lag){

  d <- data_panel %>%
    arrange(country, year_month) %>%
    group_by(country) %>%
    mutate(
      dG     = G_Trends - lag(G_Trends),
      dIV    = .data[[iv]] - lag(.data[[iv]]),
      iv_lag = lag(dIV, lag)
    ) %>%
    ungroup() %>%
    filter(
      !is.na(dG),
      !is.na(iv_lag)
    )

  if(nrow(d) < 30){
    return(tibble(
      instrument = iv,
      lag = lag,
      coef_rf = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "too_few_obs"
    ))
  }

  m <- tryCatch(
    feols(
      dG ~ iv_lag | country^year + year_month,
      data = d,
      cluster = ~country
    ),
    error = function(e) NULL
  )

  if(is.null(m)){
    return(tibble(
      instrument = iv,
      lag = lag,
      coef_rf = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "failed"
    ))
  }

  ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

  if(is.null(ct) || !("iv_lag" %in% rownames(ct))){
    return(tibble(
      instrument = iv,
      lag = lag,
      coef_rf = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "no_coef"
    ))
  }

  tibble(
    instrument = iv,
    lag = lag,
    coef_rf = ct["iv_lag", "Estimate"],
    p_value = ct["iv_lag", "Pr(>|t|)"],
    n = nrow(d),
    status = "ok"
  )
}

# -------------------------
# Differenced IV
# dG on lagged dN instrumented by lagged dIV
# -------------------------

run_iv_safe <- function(data_panel, variable, iv, lag){

  d <- data_panel %>%
    arrange(country, year_month) %>%
    group_by(country) %>%
    mutate(
      dG     = G_Trends - lag(G_Trends),
      dN     = .data[[variable]] - lag(.data[[variable]]),
      dIV    = .data[[iv]] - lag(.data[[iv]]),
      p_lag  = lag(dN, lag),
      iv_lag = lag(dIV, lag)
    ) %>%
    ungroup() %>%
    filter(
      !is.na(dG),
      !is.na(p_lag),
      !is.na(iv_lag)
    )

  if(nrow(d) < 30){
    return(tibble(
      variable = variable,
      lag = lag,
      instrument = iv,
      F_first_stage = NA_real_,
      coef_iv = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "too_few_obs"
    ))
  }

  fs <- tryCatch(
    feols(
      p_lag ~ iv_lag | country^year + year_month,
      data = d,
      cluster = ~country
    ),
    error = function(e) NULL
  )

  if(is.null(fs)){
    return(tibble(
      variable = variable,
      lag = lag,
      instrument = iv,
      F_first_stage = NA_real_,
      coef_iv = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "first_stage_failed"
    ))
  }

  ct_fs <- tryCatch(summary(fs)$coeftable, error = function(e) NULL)

  if(is.null(ct_fs) || !("iv_lag" %in% rownames(ct_fs))){
    return(tibble(
      variable = variable,
      lag = lag,
      instrument = iv,
      F_first_stage = NA_real_,
      coef_iv = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "no_first_stage_coef"
    ))
  }

  t_excl <- ct_fs["iv_lag", "t value"]
  F_fs   <- as.numeric(t_excl)^2

  ivm <- tryCatch(
    feols(
      dG ~ 1 | country^year + year_month | p_lag ~ iv_lag,
      data = d,
      cluster = ~country
    ),
    error = function(e) NULL
  )

  if(is.null(ivm)){
    return(tibble(
      variable = variable,
      lag = lag,
      instrument = iv,
      F_first_stage = F_fs,
      coef_iv = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "second_stage_failed"
    ))
  }

  ct <- tryCatch(summary(ivm)$coeftable, error = function(e) NULL)

  if(is.null(ct) || !("fit_p_lag" %in% rownames(ct))){
    return(tibble(
      variable = variable,
      lag = lag,
      instrument = iv,
      F_first_stage = F_fs,
      coef_iv = NA_real_,
      p_value = NA_real_,
      n = nrow(d),
      status = "no_second_stage_coef"
    ))
  }

  tibble(
    variable = variable,
    lag = lag,
    instrument = iv,
    F_first_stage = F_fs,
    coef_iv = ct["fit_p_lag", "Estimate"],
    p_value = ct["fit_p_lag", "Pr(>|t|)"],
    n = nrow(d),
    status = "ok"
  )
}

# -------------------------
# Run baseline reduced form
# -------------------------

rf_owner_weighted_baseline <- expand.grid(
  instrument = owner_iv_vars,
  lag = 1:12,
  stringsAsFactors = FALSE
) %>%
  pmap_dfr(~ run_rf_safe(df_weighted_owner_baseline, ..1, ..2))

rf_owner_weighted_baseline_hits <- rf_owner_weighted_baseline %>%
  filter(status == "ok", p_value < 0.1) %>%
  arrange(p_value)

# -------------------------
# Run discounted reduced form
# -------------------------

rf_owner_weighted_discounted <- expand.grid(
  instrument = owner_iv_vars,
  lag = 1:12,
  stringsAsFactors = FALSE
) %>%
  pmap_dfr(~ run_rf_safe(df_weighted_owner_discounted, ..1, ..2))

rf_owner_weighted_discounted_hits <- rf_owner_weighted_discounted %>%
  filter(status == "ok", p_value < 0.1) %>%
  arrange(p_value)

# -------------------------
# Run baseline IV
# -------------------------

results_iv_owner_weighted_baseline <- expand.grid(
  variable = weighted_narratives_baseline,
  lag = 1:12,
  instrument = owner_iv_vars,
  stringsAsFactors = FALSE
) %>%
  pmap_dfr(~ run_iv_safe(df_weighted_owner_baseline, ..1, ..3, ..2))

strong_iv_owner_weighted_baseline <- results_iv_owner_weighted_baseline %>%
  filter(status == "ok", F_first_stage > 5, p_value < 0.1) %>%
  arrange(desc(F_first_stage), p_value)

iv_owner_weighted_baseline_summary <- strong_iv_owner_weighted_baseline %>%
  label_results() %>%
  mutate(
    coef = round(coef_iv, 3),
    p_value = round(p_value, 3),
    F_stat = round(F_first_stage, 2)
  ) %>%
  select(narrative, type, lag, instrument, coef, p_value, F_stat, n) %>%
  arrange(desc(F_stat), p_value)

# -------------------------
# Run discounted IV
# -------------------------

results_iv_owner_weighted_discounted <- expand.grid(
  variable = weighted_narratives_discounted,
  lag = 1:12,
  instrument = owner_iv_vars,
  stringsAsFactors = FALSE
) %>%
  pmap_dfr(~ run_iv_safe(df_weighted_owner_discounted, ..1, ..3, ..2))

strong_iv_owner_weighted_discounted <- results_iv_owner_weighted_discounted %>%
  filter(status == "ok", F_first_stage > 5, p_value < 0.1) %>%
  arrange(desc(F_first_stage), p_value)

iv_owner_weighted_discounted_summary <- strong_iv_owner_weighted_discounted %>%
  label_results() %>%
  mutate(
    coef = round(coef_iv, 3),
    p_value = round(p_value, 3),
    F_stat = round(F_first_stage, 2)
  ) %>%
  select(narrative, type, lag, instrument, coef, p_value, F_stat, n) %>%
  arrange(desc(F_stat), p_value)

# -------------------------
# Overlap table: specs that survive both
# -------------------------

baseline_clean <- strong_iv_owner_weighted_baseline %>%
  label_results() %>%
  select(narrative, type, lag, instrument,
         coef_base = coef_iv,
         p_base = p_value,
         F_base = F_first_stage)

discounted_clean <- strong_iv_owner_weighted_discounted %>%
  label_results() %>%
  select(narrative, type, lag, instrument,
         coef_disc = coef_iv,
         p_disc = p_value,
         F_disc = F_first_stage)

robust_iv_specs <- baseline_clean %>%
  inner_join(
    discounted_clean,
    by = c("narrative", "type", "lag", "instrument")
  ) %>%
  mutate(
    coef_base = round(coef_base, 3),
    coef_disc = round(coef_disc, 3),
    p_base    = round(p_base, 3),
    p_disc    = round(p_disc, 3),
    F_base    = round(F_base, 2),
    F_disc    = round(F_disc, 2),
    coef_diff = round(coef_disc - coef_base, 3)
  ) %>%
  arrange(desc(F_base), desc(F_disc))

robust_iv_summary <- robust_iv_specs %>%
  select(
    narrative, type, lag, instrument,
    coef_base, coef_disc,
    F_base, F_disc,
    p_base, p_disc
  )

write.csv(rf_owner_weighted_baseline, "rf_owner_weighted_baseline.csv", row.names = FALSE)
write.csv(rf_owner_weighted_discounted, "rf_owner_weighted_discounted.csv", row.names = FALSE)

write.csv(results_iv_owner_weighted_baseline, "results_iv_owner_weighted_baseline.csv", row.names = FALSE)
write.csv(results_iv_owner_weighted_discounted, "results_iv_owner_weighted_discounted.csv", row.names = FALSE)

write.csv(iv_owner_weighted_baseline_summary, "iv_owner_weighted_baseline_summary.csv", row.names = FALSE)
write.csv(iv_owner_weighted_discounted_summary, "iv_owner_weighted_discounted_summary.csv", row.names = FALSE)

write.csv(robust_iv_summary, "robust_iv_summary.csv", row.names = FALSE)
```

```{r}
# -------------------------
# Electoral competition model with weighted and aggregated data
# -------------------------

country_map <- tibble::tribble(
  ~iso2, ~country_name,    ~system,
  "AU",  "Australia",      "parliamentary",
  "BD",  "Bangladesh",     "parliamentary",
  "CA",  "Canada",         "parliamentary",
  "GB",  "UK",             "parliamentary",
  "GH",  "Ghana",          "presidential",
  "HK",  NA_character_,    "none",
  "IE",  "Ireland",        "parliamentary",
  "IN",  "India",          "parliamentary",
  "JM",  "Jamaica",        "parliamentary",
  "KE",  "Kenya",          "presidential",
  "LK",  "Sri Lanka",      "presidential",
  "MY",  "Malaysia",       "parliamentary",
  "NG",  "Nigeria",        "presidential",
  "NZ",  "New Zealand",    "parliamentary",
  "PH",  "Philippines",    "presidential",
  "PK",  "Pakistan",       "parliamentary",
  "SG",  "Singapore",      "parliamentary",
  "TZ",  "Tanzania",       "presidential",
  "US",  "USA",            "presidential",
  "ZA",  "S. Africa",      "parliamentary"
)

target_iso2 <- c("AU","BD","CA","GB","GH","HK","IE","IN","JM","KE",
                 "LK","MY","NG","NZ","PH","PK","SG","TZ","US","ZA")

target_months <- seq(as.Date("2011-01-01"), as.Date("2024-12-01"), by = "month")

make_election_date <- function(date_col, year_col, month_col = NULL) {
  out <- suppressWarnings(as.Date(date_col))
  if (!is.null(month_col)) {
    fallback <- as.Date(sprintf("%s-%02d-01", year_col, ifelse(is.na(month_col), 6, as.integer(month_col))))
  } else {
    fallback <- as.Date(sprintf("%s-06-01", year_col))
  }
  ifelse(is.na(out), fallback, out) |> as.Date(origin = "1970-01-01")
}

parl_raw <- read_dta("parliamentary_elections_v2.dta")
pres_raw <- read_dta("presidential_elections_v2.dta")

parl_keep <- country_map %>%
  filter(system == "parliamentary") %>%
  pull(country_name)

parl_elections <- parl_raw %>%
  filter(country %in% parl_keep) %>%
  mutate(
    election_id = row_number(),
    election_date = make_election_date(date, year, month)
  ) %>%
  select(election_id, country, year, election_date, matches("^(party|seat_share)_[0-9]+$")) %>%
  pivot_longer(
    cols = matches("^(party|seat_share)_[0-9]+$"),
    names_to = c(".value", "slot"),
    names_pattern = "^(party|seat_share)_([0-9]+)$"
  ) %>%
  mutate(
    slot = as.integer(slot),
    seat_share = suppressWarnings(as.numeric(seat_share))
  ) %>%
  filter(!is.na(seat_share), seat_share > 0) %>%
  group_by(election_id, country, year, election_date) %>%
  arrange(desc(seat_share), .by_group = TRUE) %>%
  mutate(rank = row_number()) %>%
  filter(rank <= 2) %>%
  summarise(
    top1_name = party[rank == 1][1],
    top1_share = seat_share[rank == 1][1],
    top2_name = party[rank == 2][1],
    top2_share = seat_share[rank == 2][1],
    margin_pp = abs(top1_share - top2_share),
    metric_used = "seat_share",
    .groups = "drop"
  ) %>%
  left_join(country_map %>% select(iso2, country_name), by = c("country" = "country_name")) %>%
  select(iso2, country, election_date, year, top1_name, top1_share, top2_name, top2_share, margin_pp, metric_used)

pres_keep <- country_map %>%
  filter(system == "presidential") %>%
  pull(country_name)

pres_elections <- pres_raw %>%
  filter(country %in% pres_keep) %>%
  mutate(
    election_id = row_number(),
    election_date = make_election_date(date, year, month)
  ) %>%
  select(election_id, country, year, election_date, matches("^(candidate|party|vote_share1|vote_share2)_[0-9]+$")) %>%
  pivot_longer(
    cols = matches("^(candidate|party|vote_share1|vote_share2)_[0-9]+$"),
    names_to = c(".value", "slot"),
    names_pattern = "^(candidate|party|vote_share1|vote_share2)_([0-9]+)$"
  ) %>%
  mutate(
    slot = as.integer(slot),
    vote_share1 = suppressWarnings(as.numeric(vote_share1)),
    vote_share2 = suppressWarnings(as.numeric(vote_share2)),
    final_share = ifelse(!is.na(vote_share2), vote_share2, vote_share1),
    label = dplyr::coalesce(candidate, party)
  ) %>%
  filter(!is.na(final_share), final_share > 0) %>%
  group_by(election_id, country, year, election_date) %>%
  arrange(desc(final_share), .by_group = TRUE) %>%
  mutate(rank = row_number()) %>%
  filter(rank <= 2) %>%
  summarise(
    top1_name = label[rank == 1][1],
    top1_share = final_share[rank == 1][1],
    top2_name = label[rank == 2][1],
    top2_share = final_share[rank == 2][1],
    margin_pp = abs(top1_share - top2_share),
    metric_used = ifelse(any(!is.na(vote_share2)), "vote_share_round2_if_available_else_round1", "vote_share_round1"),
    .groups = "drop"
  ) %>%
  left_join(country_map %>% select(iso2, country_name), by = c("country" = "country_name")) %>%
  select(iso2, country, election_date, year, top1_name, top1_share, top2_name, top2_share, margin_pp, metric_used)

election_margins <- bind_rows(parl_elections, pres_elections) %>%
  distinct(iso2, election_date, .keep_all = TRUE) %>%
  arrange(iso2, election_date)

monthly_panel <- tidyr::expand_grid(
  iso2 = target_iso2,
  month_date = target_months
)

last_election_panel <- monthly_panel %>%
  left_join(election_margins, by = "iso2") %>%
  filter(is.na(election_date) | election_date <= month_date) %>%
  group_by(iso2, month_date) %>%
  slice_max(order_by = election_date, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    iso2,
    month_date,
    last_election_date = election_date,
    last_election_year = year,
    last_top1_name = top1_name,
    last_top1_share = top1_share,
    last_top2_name = top2_name,
    last_top2_share = top2_share,
    last_election_margin_pp = margin_pp,
    metric_used
  )

next_election_panel <- monthly_panel %>%
  left_join(election_margins %>% select(iso2, election_date), by = "iso2") %>%
  filter(is.na(election_date) | election_date >= month_date) %>%
  group_by(iso2, month_date) %>%
  slice_min(order_by = election_date, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  transmute(
    iso2,
    month_date,
    next_election_date = election_date
  )

competition_merge_ready <- monthly_panel %>%
  left_join(last_election_panel, by = c("iso2", "month_date")) %>%
  left_join(next_election_panel, by = c("iso2", "month_date")) %>%
  left_join(country_map %>% select(iso2, system), by = "iso2") %>%
  mutate(
    months_since_last_election = ifelse(
      !is.na(last_election_date),
      12 * (year(month_date) - year(last_election_date)) + (month(month_date) - month(last_election_date)),
      NA_real_
    ),
    months_to_next_election = ifelse(
      !is.na(next_election_date),
      12 * (year(next_election_date) - year(month_date)) + (month(next_election_date) - month(month_date)),
      NA_real_
    ),
    election_month = ifelse(!is.na(last_election_date) & floor_date(month_date, "month") == floor_date(last_election_date, "month"), 1L, 0L),
    close_race_5pp = ifelse(!is.na(last_election_margin_pp) & last_election_margin_pp < 5, 1L, 0L),
    close_race_10pp = ifelse(!is.na(last_election_margin_pp) & last_election_margin_pp < 10, 1L, 0L),
    month = format(month_date, "%Y-%m")
  ) %>%
  select(
    iso2,
    month,
    system,
    metric_used,
    last_election_date,
    next_election_date,
    months_since_last_election,
    months_to_next_election,
    election_month,
    last_top1_name,
    last_top1_share,
    last_top2_name,
    last_top2_share,
    last_election_margin_pp,
    close_race_5pp,
    close_race_10pp
  ) %>%
  arrange(iso2, month)

write.csv(competition_merge_ready, "competition_merge_ready_2011_2024.csv", row.names = FALSE)

df_weighted_owner_baseline_ec <- df_weighted_owner_baseline %>%
  left_join(
    competition_merge_ready %>%
      rename(country = iso2, year_month = month),
    by = c("country", "year_month")
  ) %>%
  mutate(
    close_race_5pp = as.numeric(close_race_5pp),
    close_race_10pp = as.numeric(close_race_10pp),
    election_month = as.numeric(election_month),
    near_election_12m = ifelse(!is.na(months_to_next_election) & months_to_next_election <= 12, 1, 0),
    near_election_6m = ifelse(!is.na(months_to_next_election) & months_to_next_election <= 6, 1, 0),
    high_competition_cont = ifelse(!is.na(last_election_margin_pp), -last_election_margin_pp, NA_real_)
  )

df_weighted_owner_discounted_ec <- df_weighted_owner_discounted %>%
  left_join(
    competition_merge_ready %>%
      rename(country = iso2, year_month = month),
    by = c("country", "year_month")
  ) %>%
  mutate(
    close_race_5pp = as.numeric(close_race_5pp),
    close_race_10pp = as.numeric(close_race_10pp),
    election_month = as.numeric(election_month),
    near_election_12m = ifelse(!is.na(months_to_next_election) & months_to_next_election <= 12, 1, 0),
    near_election_6m = ifelse(!is.na(months_to_next_election) & months_to_next_election <= 6, 1, 0),
    high_competition_cont = ifelse(!is.na(last_election_margin_pp), -last_election_margin_pp, NA_real_)
  )

run_lags_diff_close_race_interaction <- function(data_panel, vars, L_max = 12, spec_name = "close_race") {
  purrr::map_dfr(vars, function(var) {
    purrr::map_dfr(1:L_max, function(L) {
      d <- data_panel %>%
        arrange(country, year_month) %>%
        group_by(country) %>%
        mutate(
          dG = G_Trends - lag(G_Trends),
          dN = .data[[var]] - lag(.data[[var]]),
          p_lag = lag(dN, L)
        ) %>%
        ungroup() %>%
        filter(
          !is.na(dG),
          !is.na(p_lag),
          !is.na(close_race_5pp)
        )

      if(nrow(d) < 30){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "too_few_obs"
        ))
      }

      m <- tryCatch(
        feols(
          dG ~ p_lag * close_race_5pp | country^year,
          data = d,
          cluster = ~country
        ),
        error = function(e) NULL
      )

      if(is.null(m)){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "failed"
        ))
      }

      ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

      if(is.null(ct) || !("p_lag" %in% rownames(ct)) || !("p_lag:close_race_5pp" %in% rownames(ct))){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "no_coef"
        ))
      }

      tibble(
        variable = var,
        lag = L,
        coef_p_lag = ct["p_lag", "Estimate"],
        p_p_lag = ct["p_lag", "Pr(>|t|)"],
        coef_inter = ct["p_lag:close_race_5pp", "Estimate"],
        p_inter = ct["p_lag:close_race_5pp", "Pr(>|t|)"],
        n = nrow(d),
        spec = spec_name,
        status = "ok"
      )
    })
  })
}

run_lags_diff_near_election_interaction <- function(data_panel, vars, L_max = 12, spec_name = "near_election") {
  purrr::map_dfr(vars, function(var) {
    purrr::map_dfr(1:L_max, function(L) {
      d <- data_panel %>%
        arrange(country, year_month) %>%
        group_by(country) %>%
        mutate(
          dG = G_Trends - lag(G_Trends),
          dN = .data[[var]] - lag(.data[[var]]),
          p_lag = lag(dN, L)
        ) %>%
        ungroup() %>%
        filter(
          !is.na(dG),
          !is.na(p_lag),
          !is.na(near_election_12m)
        )

      if(nrow(d) < 30){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "too_few_obs"
        ))
      }

      m <- tryCatch(
        feols(
          dG ~ p_lag * near_election_12m | country^year,
          data = d,
          cluster = ~country
        ),
        error = function(e) NULL
      )

      if(is.null(m)){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "failed"
        ))
      }

      ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

      if(is.null(ct) || !("p_lag" %in% rownames(ct)) || !("p_lag:near_election_12m" %in% rownames(ct))){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "no_coef"
        ))
      }

      tibble(
        variable = var,
        lag = L,
        coef_p_lag = ct["p_lag", "Estimate"],
        p_p_lag = ct["p_lag", "Pr(>|t|)"],
        coef_inter = ct["p_lag:near_election_12m", "Estimate"],
        p_inter = ct["p_lag:near_election_12m", "Pr(>|t|)"],
        n = nrow(d),
        spec = spec_name,
        status = "ok"
      )
    })
  })
}

run_lags_diff_margin_interaction <- function(data_panel, vars, L_max = 12, spec_name = "margin") {
  purrr::map_dfr(vars, function(var) {
    purrr::map_dfr(1:L_max, function(L) {
      d <- data_panel %>%
        arrange(country, year_month) %>%
        group_by(country) %>%
        mutate(
          dG = G_Trends - lag(G_Trends),
          dN = .data[[var]] - lag(.data[[var]]),
          p_lag = lag(dN, L)
        ) %>%
        ungroup() %>%
        filter(
          !is.na(dG),
          !is.na(p_lag),
          !is.na(last_election_margin_pp)
        )

      if(nrow(d) < 30){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "too_few_obs"
        ))
      }

      m <- tryCatch(
        feols(
          dG ~ p_lag * last_election_margin_pp | country^year,
          data = d,
          cluster = ~country
        ),
        error = function(e) NULL
      )

      if(is.null(m)){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "failed"
        ))
      }

      ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

      if(is.null(ct) || !("p_lag" %in% rownames(ct)) || !("p_lag:last_election_margin_pp" %in% rownames(ct))){
        return(tibble(
          variable = var,
          lag = L,
          coef_p_lag = NA_real_,
          p_p_lag = NA_real_,
          coef_inter = NA_real_,
          p_inter = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "no_coef"
        ))
      }

      tibble(
        variable = var,
        lag = L,
        coef_p_lag = ct["p_lag", "Estimate"],
        p_p_lag = ct["p_lag", "Pr(>|t|)"],
        coef_inter = ct["p_lag:last_election_margin_pp", "Estimate"],
        p_inter = ct["p_lag:last_election_margin_pp", "Pr(>|t|)"],
        n = nrow(d),
        spec = spec_name,
        status = "ok"
      )
    })
  })
}

run_same_sample_baseline_close <- function(data_panel, vars, L_max = 12, spec_name = "baseline_close_sample") {
  purrr::map_dfr(vars, function(var) {
    purrr::map_dfr(1:L_max, function(L) {
      d <- data_panel %>%
        arrange(country, year_month) %>%
        group_by(country) %>%
        mutate(
          dG = G_Trends - lag(G_Trends),
          dN = .data[[var]] - lag(.data[[var]]),
          p_lag = lag(dN, L)
        ) %>%
        ungroup() %>%
        filter(
          !is.na(dG),
          !is.na(p_lag),
          !is.na(close_race_5pp)
        )

      m <- tryCatch(
        feols(
          dG ~ p_lag | country^year,
          data = d,
          cluster = ~country
        ),
        error = function(e) NULL
      )

      if(is.null(m)){
        return(tibble(
          variable = var,
          lag = L,
          coef = NA_real_,
          p_value = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "failed"
        ))
      }

      ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

      if(is.null(ct) || !("p_lag" %in% rownames(ct))){
        return(tibble(
          variable = var,
          lag = L,
          coef = NA_real_,
          p_value = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "no_coef"
        ))
      }

      tibble(
        variable = var,
        lag = L,
        coef = ct["p_lag", "Estimate"],
        p_value = ct["p_lag", "Pr(>|t|)"],
        n = nrow(d),
        spec = spec_name,
        status = "ok"
      )
    })
  })
}

run_same_sample_baseline_near <- function(data_panel, vars, L_max = 12, spec_name = "baseline_near_sample") {
  purrr::map_dfr(vars, function(var) {
    purrr::map_dfr(1:L_max, function(L) {
      d <- data_panel %>%
        arrange(country, year_month) %>%
        group_by(country) %>%
        mutate(
          dG = G_Trends - lag(G_Trends),
          dN = .data[[var]] - lag(.data[[var]]),
          p_lag = lag(dN, L)
        ) %>%
        ungroup() %>%
        filter(
          !is.na(dG),
          !is.na(p_lag),
          !is.na(near_election_12m)
        )

      m <- tryCatch(
        feols(
          dG ~ p_lag | country^year,
          data = d,
          cluster = ~country
        ),
        error = function(e) NULL
      )

      if(is.null(m)){
        return(tibble(
          variable = var,
          lag = L,
          coef = NA_real_,
          p_value = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "failed"
        ))
      }

      ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

      if(is.null(ct) || !("p_lag" %in% rownames(ct))){
        return(tibble(
          variable = var,
          lag = L,
          coef = NA_real_,
          p_value = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "no_coef"
        ))
      }

      tibble(
        variable = var,
        lag = L,
        coef = ct["p_lag", "Estimate"],
        p_value = ct["p_lag", "Pr(>|t|)"],
        n = nrow(d),
        spec = spec_name,
        status = "ok"
      )
    })
  })
}

run_same_sample_baseline_margin <- function(data_panel, vars, L_max = 12, spec_name = "baseline_margin_sample") {
  purrr::map_dfr(vars, function(var) {
    purrr::map_dfr(1:L_max, function(L) {
      d <- data_panel %>%
        arrange(country, year_month) %>%
        group_by(country) %>%
        mutate(
          dG = G_Trends - lag(G_Trends),
          dN = .data[[var]] - lag(.data[[var]]),
          p_lag = lag(dN, L)
        ) %>%
        ungroup() %>%
        filter(
          !is.na(dG),
          !is.na(p_lag),
          !is.na(last_election_margin_pp)
        )

      m <- tryCatch(
        feols(
          dG ~ p_lag | country^year,
          data = d,
          cluster = ~country
        ),
        error = function(e) NULL
      )

      if(is.null(m)){
        return(tibble(
          variable = var,
          lag = L,
          coef = NA_real_,
          p_value = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "failed"
        ))
      }

      ct <- tryCatch(summary(m)$coeftable, error = function(e) NULL)

      if(is.null(ct) || !("p_lag" %in% rownames(ct))){
        return(tibble(
          variable = var,
          lag = L,
          coef = NA_real_,
          p_value = NA_real_,
          n = nrow(d),
          spec = spec_name,
          status = "no_coef"
        ))
      }

      tibble(
        variable = var,
        lag = L,
        coef = ct["p_lag", "Estimate"],
        p_value = ct["p_lag", "Pr(>|t|)"],
        n = nrow(d),
        spec = spec_name,
        status = "ok"
      )
    })
  })
}

results_close_race_weighted_baseline <- run_lags_diff_close_race_interaction(
  data_panel = df_weighted_owner_baseline_ec,
  vars = weighted_narratives_baseline,
  L_max = 12,
  spec_name = "close_race_weighted_baseline"
)

results_near_election_weighted_baseline <- run_lags_diff_near_election_interaction(
  data_panel = df_weighted_owner_baseline_ec,
  vars = weighted_narratives_baseline,
  L_max = 12,
  spec_name = "near_election_weighted_baseline"
)

results_margin_weighted_baseline <- run_lags_diff_margin_interaction(
  data_panel = df_weighted_owner_baseline_ec,
  vars = weighted_narratives_baseline,
  L_max = 12,
  spec_name = "margin_weighted_baseline"
)

results_close_race_weighted_discounted <- run_lags_diff_close_race_interaction(
  data_panel = df_weighted_owner_discounted_ec,
  vars = weighted_narratives_discounted,
  L_max = 12,
  spec_name = "close_race_weighted_discounted"
)

results_near_election_weighted_discounted <- run_lags_diff_near_election_interaction(
  data_panel = df_weighted_owner_discounted_ec,
  vars = weighted_narratives_discounted,
  L_max = 12,
  spec_name = "near_election_weighted_discounted"
)

results_margin_weighted_discounted <- run_lags_diff_margin_interaction(
  data_panel = df_weighted_owner_discounted_ec,
  vars = weighted_narratives_discounted,
  L_max = 12,
  spec_name = "margin_weighted_discounted"
)

baseline_close_sample_weighted_baseline <- run_same_sample_baseline_close(
  data_panel = df_weighted_owner_baseline_ec,
  vars = weighted_narratives_baseline,
  L_max = 12,
  spec_name = "baseline_close_sample_weighted_baseline"
)

baseline_near_sample_weighted_baseline <- run_same_sample_baseline_near(
  data_panel = df_weighted_owner_baseline_ec,
  vars = weighted_narratives_baseline,
  L_max = 12,
  spec_name = "baseline_near_sample_weighted_baseline"
)

baseline_margin_sample_weighted_baseline <- run_same_sample_baseline_margin(
  data_panel = df_weighted_owner_baseline_ec,
  vars = weighted_narratives_baseline,
  L_max = 12,
  spec_name = "baseline_margin_sample_weighted_baseline"
)

baseline_close_sample_weighted_discounted <- run_same_sample_baseline_close(
  data_panel = df_weighted_owner_discounted_ec,
  vars = weighted_narratives_discounted,
  L_max = 12,
  spec_name = "baseline_close_sample_weighted_discounted"
)

baseline_near_sample_weighted_discounted <- run_same_sample_baseline_near(
  data_panel = df_weighted_owner_discounted_ec,
  vars = weighted_narratives_discounted,
  L_max = 12,
  spec_name = "baseline_near_sample_weighted_discounted"
)

baseline_margin_sample_weighted_discounted <- run_same_sample_baseline_margin(
  data_panel = df_weighted_owner_discounted_ec,
  vars = weighted_narratives_discounted,
  L_max = 12,
  spec_name = "baseline_margin_sample_weighted_discounted"
)

close_race_weighted_baseline_hits <- results_close_race_weighted_baseline %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(p_inter)

near_election_weighted_baseline_hits <- results_near_election_weighted_baseline %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(p_inter)

margin_weighted_baseline_hits <- results_margin_weighted_baseline %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(p_inter)

close_race_weighted_discounted_hits <- results_close_race_weighted_discounted %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(p_inter)

near_election_weighted_discounted_hits <- results_near_election_weighted_discounted %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(p_inter)

margin_weighted_discounted_hits <- results_margin_weighted_discounted %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(p_inter)

interaction_results_weighted_baseline <- bind_rows(
  results_close_race_weighted_baseline,
  results_near_election_weighted_baseline,
  results_margin_weighted_baseline
)

interaction_results_weighted_discounted <- bind_rows(
  results_close_race_weighted_discounted,
  results_near_election_weighted_discounted,
  results_margin_weighted_discounted
)

interaction_hits_weighted_baseline <- interaction_results_weighted_baseline %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(spec, p_inter)

interaction_hits_weighted_discounted <- interaction_results_weighted_discounted %>%
  filter(status == "ok", p_inter < 0.1) %>%
  label_results() %>%
  arrange(spec, p_inter)

compare_close_race_weighted_baseline <- results_close_race_weighted_baseline %>%
  filter(status == "ok") %>%
  left_join(
    baseline_close_sample_weighted_baseline %>%
      filter(status == "ok") %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_non_close = coef_p_lag,
    effect_close_race = coef_p_lag + coef_inter
  )

compare_near_election_weighted_baseline <- results_near_election_weighted_baseline %>%
  filter(status == "ok") %>%
  left_join(
    baseline_near_sample_weighted_baseline %>%
      filter(status == "ok") %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_non_election = coef_p_lag,
    effect_near_election = coef_p_lag + coef_inter
  )

compare_margin_weighted_baseline <- results_margin_weighted_baseline %>%
  filter(status == "ok") %>%
  left_join(
    baseline_margin_sample_weighted_baseline %>%
      filter(status == "ok") %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_high_competition = coef_p_lag + coef_inter * 5,
    effect_medium_competition = coef_p_lag + coef_inter * 10,
    effect_low_competition = coef_p_lag + coef_inter * 20
  )

compare_close_race_weighted_discounted <- results_close_race_weighted_discounted %>%
  filter(status == "ok") %>%
  left_join(
    baseline_close_sample_weighted_discounted %>%
      filter(status == "ok") %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_non_close = coef_p_lag,
    effect_close_race = coef_p_lag + coef_inter
  )

compare_near_election_weighted_discounted <- results_near_election_weighted_discounted %>%
  filter(status == "ok") %>%
  left_join(
    baseline_near_sample_weighted_discounted %>%
      filter(status == "ok") %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_non_election = coef_p_lag,
    effect_near_election = coef_p_lag + coef_inter
  )

compare_margin_weighted_discounted <- results_margin_weighted_discounted %>%
  filter(status == "ok") %>%
  left_join(
    baseline_margin_sample_weighted_discounted %>%
      filter(status == "ok") %>%
      select(variable, lag, coef_base = coef, p_base = p_value),
    by = c("variable", "lag")
  ) %>%
  mutate(
    effect_high_competition = coef_p_lag + coef_inter * 5,
    effect_medium_competition = coef_p_lag + coef_inter * 10,
    effect_low_competition = coef_p_lag + coef_inter * 20
  )

df_weighted_owner_baseline_ec %>%
  summarise(
    n_obs = n(),
    n_close_race_nonmissing = sum(!is.na(close_race_5pp)),
    n_margin_nonmissing = sum(!is.na(last_election_margin_pp)),
    n_near_election_nonmissing = sum(!is.na(near_election_12m))
  )

df_weighted_owner_baseline_ec %>%
  group_by(country) %>%
  summarise(
    n_obs = n(),
    n_close_race_nonmissing = sum(!is.na(close_race_5pp)),
    n_margin_nonmissing = sum(!is.na(last_election_margin_pp)),
    .groups = "drop"
  ) %>%
  arrange(country)

df_weighted_owner_discounted_ec %>%
  summarise(
    n_obs = n(),
    n_close_race_nonmissing = sum(!is.na(close_race_5pp)),
    n_margin_nonmissing = sum(!is.na(last_election_margin_pp)),
    n_near_election_nonmissing = sum(!is.na(near_election_12m))
  )

df_weighted_owner_discounted_ec %>%
  group_by(country) %>%
  summarise(
    n_obs = n(),
    n_close_race_nonmissing = sum(!is.na(close_race_5pp)),
    n_margin_nonmissing = sum(!is.na(last_election_margin_pp)),
    .groups = "drop"
  ) %>%
  arrange(country)
```
